My title

### 2024-11-01 paper/paper.qmd

>>>>

## Objective
The survey aims to precisely capture voter intention and mood across important demographic and geographic divisions in order to predict the result of the US presidential election.

## Sampling Approach
* Stratified Random Sampling: To replicate the national electorate, stratify the sample according to age, gender, race/ethnicity, education level, urban/rural domicile, and area.

* Sample Size: Aim for a starting sample of five thousand people. This results in around 2000 to 2500 replies every wave, assuming a response rate of 40–50%.

## Respondent Recruitment
* Panel Providers: Partner with an online panel provider to find respondents that match each stratum’s specifications.Specify quotas to ensure that, for instance, you have 18% of respondents from the Midwest or 25% aging between 30 - 40.

* Random Sampling: Randomly select respondent within each strata.

* Incentives: To promote greater response rates and retention, provide a small monetary reward, such as $5 to $10 for each completed survey.

* Multi-Mode: To improve inclusivity and take into consideration differences in internet availability, use both phone and online surveys.

## Data Validation
* De-duplication: To keep distinct replies between waves, make sure respondents don't participate more than once each wave.

* Quality checks: highlight straight-lining, inconsistent replies, and other low-effort answers.

## Essential Questions
* Are you currently registered to vote?
  - Yes
  - No

* Which state are you currently registered to vote in?
  (short answer)

* Do you plan to vote in the upcoming Presidential election?
  - Yes, I plan to vote in person on election day
  - Yes, I plan to vote in person early
  - Yes, I plan to vote by mail
  - No, I do not plan to vote

* If the election were held today, who would you vote for?
  - Democrat Kamala Harris
  - Republican Donald Trump
  - A third party / Independent candidate
  - Unsure

* How certain are you about your choice
  - Scale 1 to 5

* Your gender idetification
  - Female
  - Male
  - Other

* Age Range
  - 18 to 24
  - 25 to 29
  - 30 to 39
  - 40 to 49
  - 50 to 59
  - 60 or older

* Which of the following best describes your racial background?
  - White or Caucasion
  - Black or African American
  - Hispanic
  - Asian or Pacific Islander
  - Native American
  - Other

* How would you describe your educational level
  - High School or less
  - College Graduate
  - Post-graduate degree
  - Unsure

* Employment Status
  - Full time
  - Part time
  - Unemployed

* What's your estimated household income?
  - Under $30,000
  - \$30k - \$49,999
  - \$50k - \$99,999
  - \$100k - \$199,999
  - \$200k - \$249,999
  - \$250k or more
  - Unsure

* Do you consider yourself to be lesbian, gay, bisexual, transgender, queer or
questioning?
  - Yes
  - No
  - Unsure
  - Prefer not to answer

* Would you best describe the neighborhood or area you live in as
  - Urban
  - Suburban
  - Rural
  - Unsure

* What is your religious background
  - Religious
  - Spiritual
  - Not religious or spiritual

Link to the survey: https://forms.gle/spJjASENRQ6nKK1E6
